On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2024-07-25 char-4k-bound/char-4k-bound.tex
[4k3] 11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3 -> rails_3_8

For the sake of completeness, on Figure~\ref{fig:11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}
we give an example of rails set
with 3 points on one line and 8 points on the other (first presented in~\cite[Figure 1]{avdeev2019particular})
whose characteristic is
\begin{equation}
	255255 = 3 \cdot 5 \cdot 7 \cdot 11 \cdot 13 \cdot 17
	 = 4 \cdot 63813  + 3
\end{equation}
and whose coordinates are
\begin{multline}
\mathcal{P}_{3,8}=\sqrt{255255}/2*\{
	( 1767 ; -3);
	( 2791 ; -3);
	( 4071 ; -3);
\\
	( -306 ; 0);
	( 0 ; 0);
	( 1798 ; 0);
	( 2304 ; 0);
	( 2760 ; 0);
	( 3534 ; 0);
	( 4040 ; 0);
	( 4558 ; 0)
\}
\end{multline}

\begin{figure}
\center{\includegraphics[width=0.95\linewidth]{11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}}
\caption{The rails set with characteristic 255255}
\label{fig:11_2432_255255_a0a1b7f805cfc93080b4608505a0f45d_rails_3.png}
\end{figure}

>>>>

For the sake of completeness, on Figure~\ref{fig:rails_3_8.png}
we give an example of rails set
with 3 points on one line and 8 points on the other (first presented in~\cite[Figure 1]{avdeev2019particular})
whose characteristic is
\begin{equation}
	255255 = 3 \cdot 5 \cdot 7 \cdot 11 \cdot 13 \cdot 17
	 = 4 \cdot 63813  + 3
\end{equation}
and whose coordinates are
\begin{multline}
\mathcal{P}_{3,8}=\sqrt{255255}/2*\{
	( 1767 ; -3);
	( 2791 ; -3);
	( 4071 ; -3);
\\
	( -306 ; 0);
	( 0 ; 0);
	( 1798 ; 0);
	( 2304 ; 0);
	( 2760 ; 0);
	( 3534 ; 0);
	( 4040 ; 0);
	( 4558 ; 0)
\}
\end{multline}

\begin{figure}
\center{\includegraphics[width=0.95\linewidth]{rails_3_8.png}}
\caption{The rails set with characteristic 255255}
\label{fig:rails_3_8.png}
\end{figure}
